Probability

### 2016-04-27 prob.tex
prob.tex Updating definition of Projection Operators...

\begin{definition}[Projection Operators; Orthogonality; Commutativity]
  Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear
  transformation from $\Hilb$ to itself such that $P^2 = P$. An
  orthogonal projection furthermore satisfies $P = P^*$. Projection
  operators have the following properties:
\begin{itemize}
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$;
\item Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
\item If the projections $P_1$ and $P_2$ are orthogonal then f $P_1 +
  P_2$ is also a projection;
\item If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection; it is not sufficient in this case for $P_1$ and $P_2$
  to be orthogonal. 
\end{itemize}
\end{definition}

>>>>

\begin{definition}[Projection Operators; Orthogonality;
Commutativity~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
Given a Hilbert space $\Hilb$, a projection operator $P$ is a linear transformation from $\Hilb$
to itself such that $P^2 = P^{\dagger} = P$. Projection operators have the
following properties:\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasis $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$;
\item Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
\item If the projections $P_1$ and $P_2$ are orthogonal then f $P_1 +
  P_2$ is also a projection;
\item If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection; it is not sufficient in this case for $P_1$ and $P_2$
  to be orthogonal. 
\end{itemize}
\end{definition}
